Argennon: A Scalable Smart Contract Platform

### 2021-07-12 tex/sections/argon.tex
Re-add Argon chapter
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

@@

Argon Programs are organized as sets of packages. Each package has its own set of names for types, which helps
to prevent name conflicts. Every package can contain an arbitrary number of classes and a single contract. Every
Argon package corresponds to at max one AVM smart contract.

@@

\subsection{Static Classes}\label{subsec:static-classes}

In Argon a static class is an uninstantiable class which all its members and methods are static. Every static
class can define a special method \texttt{initialize} which can only be called in the \texttt{initialize}
method of the single contract of the package the static class is defined in.

A Static class is like a normal class which can only have one instance. So like normal classes, static classes can
be a super class or a subclass of other static classes and can implement interfaces.

\subsection{Contracts}\label{subsec:contract}

Every package of an Argon program can have one or zero contracts. A contact is a special static class which is
allowed to define methods with \texttt{external} visibility. When an Argon package is deployed as an AVM smart
contract, these external methods will define the contract's public interface.

@@

\begin{center}
    \begin{tabular}{llllll}
        \hline
        & Class & Package & Subclass & Program & World \\
        \hline
        private   & yes   & no      & no       & no      & no    \\
        protected & yes   & no      & yes      & no      & no    \\
        package   & yes   & yes     & yes      & no      & no    \\
        public    & yes   & yes     & yes      & yes     & no    \\
        external  & no    & no      & no       & no      & yes   \\
        \hline
    \end{tabular}\label{tab:table}
\end{center}

\begin{lstlisting}[frame=TB, float, title=Argon contracts are static classes,label={lst:code1}]
// A contract is a static class and all its methods are automatically static.
contract MirrorToken {
    private SimpleToken token;
    private SimpleToken reflection;

    // `initialize` is a special static method that is called by the AVM after the code of a contract
    // is stored in the AVM code area. It can not be called after that.
    initialize(double supply1, double supply2) {
        // `new` does not create a new smart contract. It just makes an ordinary object.
        token = new SimpleToken(supply1);
        reflection = new SimpleToken(supply2);
    }

    external void transfer(account sender, account recipient,
        double amount, signature sig) {
        // Checks if the signature is issued by the sender and verifies the calling of this function
        // with the current parameters.
        sig.verifyCallBy(sender);
        token.transfer(sender, recipient, amount);
        reflection.transfer(recipient, sender, Math.sqrt(amount));
    }

    external double balanceOf(account user) { return token.balanceOf(user); }

    external double balanceOfReflection(account user) { return reflection.balanceOf(user); }
}

public static class Math {
    public double sqrt(double x) {
        return // calculate square root of x
    }
}

package class SimpleToken {
    private map(account -> double) balances;

    // The visibility of a member without an access modifier will be the same as its defining
    // class so `SimpleToken` constructor has package visibility.
    constructor(double initialSupply) {
        // initializes the object
    }

    void transfer(account sender, account recipient, double amount) {
        if (balances[sender] < amount) throw("Not enough balance.");
        // implements the required logic...
    }
    // implements other methods...
}
\end{lstlisting}

>>>>

\lstset{
    language=Java,
    morekeywords={main, initialize, constructor, external, virtual, Map, Account, signature, overrides, is, string},
    basicstyle=\small\sffamily,
    columns=fullflexible,
%   keywordstyle=\bfseries,
    breaklines=true,
    showstringspaces=false,
    mathescape
}

@@

Argon applications (i.e.\ smart contracts) are organized as sets of packages. Each package has its own set of names
for types, which helps to prevent name conflicts. Every package can contain an arbitrary number of classes.
Every Argon application is required
to have exactly one \texttt{main} method and one \texttt{initialize} method. The \texttt{main} method is the
only method of an Argon application which can be called by other smart contracts.

The \texttt{main} method is required to have a single parameter named \texttt{request}. The type of this parameter
should be \texttt{RestRequest} or \texttt{HttpRequest}. The return value of the \texttt{main} function needs to be a
\texttt{RestResponse} or \texttt{HttpResponse}.

@@

@@

\begin{center}
    \begin{tabular}{lllll}
        \hline
        & Class & Package & Subclass & Program \\
        \hline
        private   & yes   & no      & no       & no  \\
        protected & yes   & no      & yes      & no  \\
        package   & yes   & yes     & yes      & no  \\
        public    & yes   & yes     & yes      & yes \\
        \hline
    \end{tabular}\label{tab:table}
\end{center}

\begin{lstlisting}[frame=TB, float, title=A simple Argon application,label={lst:code1}]
public class MirrorToken {
    private static SimpleToken token;
    private static SimpleToken reflection;

    // `initialize` is a special static method that is called by the AVM after the code of a contract
    // is stored in the AVM code area.
    public static void initialize(double supply1, double supply2) {
        // `new` does not create a new smart contract. It just makes an ordinary object.
        token = new SimpleToken(supply1);
        reflection = new SimpleToken(supply2);
    }
    // `main` is the only method of the application (i.e. smart contract) that can be called
    // by other applications. Every application should have exactly one main method defined
    // in some class. Alternatively, the keyword `dispatcher` could be used instead of `main`.
    public static RestResponse main(RestRequest request) {
        RestResponse response = new RestResponse();
        if (request.pathMatches("/balances/{user}")) {
            Account sender = request.getParameter<Account>("user");
            if (request.operationIsPUT()) {
                sender.authorize(request.toMessage(), request.getParameter<byte[]>("sig"));
                Account recipient = request.getParameter<Account>("to");
                double amount = request.getParameter<double>("amount");
                token.transfer(sender, recipient, amount);
                reflection.transfer(recipient, sender, Math.sqrt(amount));
                return response.setStatus(Http.Status.OK);
            } else if (request.operationIsGET()) {
                response.append<double>("balance", token.balanceOf(sender));
                response.append<double>("reflection", reflection.balanceOf(user));
                return response.setStatus(Http.Status.OK);
            } else {
                return response.setStatus(Http.Status.MethodNotAllowed);
            }
        }
    }
}

package class SimpleToken {
    private Map(Account -> double) balances;

    // The visibility of a member without an access modifier will be the package level.
    constructor(double initialSupply) {
        // initializes the object
    }

    void transfer(Account sender, Account recipient, double amount) {
        if (balances[sender] < amount) throw("Not enough balance.");
        // implements the required logic...
    }
    // implements other methods...
}
\end{lstlisting}
